The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-15 document/ms.tex
placeholder for follow-up section cc @davidwhogg

\begin{floattable}
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\caption{The occurrence rate density in two radius bins \label{tab:occurrence}}
\include{ortab}
\tablenotetext{a}{$\Gamma_V = \dd^2 N/\dd\ln P\dd\ln R$; see \eq{rate-density}}
\tablenotetext{b}{$\Gamma_V$ computed assuming that one candidate is a false
positive}
\tablecomments{These values are computed in the period range 2--25~years.}
\end{deluxetable}
\end{floattable}

@@

In light of this result, we demonstrate the sensitivity of our measured
occurrence rates on contamination by computing a second constraint on
$\Gamma_V$ for each volume with one candidate removed.
In this case, \eq{rate-density} would be replaced by
\begin{eqnarray}
\tilde{\Gamma}_V &\equiv&
    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})
          - 1}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\quad.
\end{eqnarray}
These updated rates are listed in Table~\ref{tab:occurrence}.
In each case, the results are consistent within the uncertainties but the
difference can be used to get a qualitative sense of the systematic
uncertainty introduced by false positives.

@@

The population of long-period planets has been previously studied using radial
velocity, microlensing, and direct imaging surveys.
These methods all measure the occurrence rate in units of mass and semi-major
axis instead of radius and period.
Using the transit method, we do not directly measure the mass of the planet.
Instead, we must rely on a mass--radius (M--R) relationship constructed using
exoplanets with both mass and radius measurements \citep[for
example]{Weiss:2014, Wolfgang:2016, Chen:2016} to predict the expected masses
of the transiting planets.

@@

@@

>>>>

\begin{floattable}
\begin{deluxetable}{cccc}
\tabletypesize{\footnotesize}
\caption{The occurrence rate density in two radius bins \label{tab:occurrence}}
\include{ortab}
\tablenotetext{a}{$\Gamma_V = \dd^2 N/\dd\ln P\dd\ln R$; see \eq{rate-density}}
\tablenotetext{b}{$\Gamma_V$ computed assuming that one candidate is a false
positive; see \eq{rate-minus}}
\tablecomments{These values are computed in the period range 2--25~years.}
\end{deluxetable}
\end{floattable}

@@

In light of this result, we demonstrate the sensitivity of our measured
occurrence rates on contamination by computing a second constraint on
$\Gamma_V$ for each volume with one candidate removed.
In this case, \eq{rate-density} would be replaced by
\begin{eqnarray}\eqlabel{rate-minus}
\tilde{\Gamma}_V &\equiv&
    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})
          - 1}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\quad.
\end{eqnarray}
These updated rates are listed in Table~\ref{tab:occurrence}.
In each case, the results are consistent within the uncertainties but the
difference can be used to get a qualitative sense of the systematic
uncertainty introduced by false positives.

@@

The population of long-period planets has been previously studied using radial
velocity, microlensing, and direct imaging surveys.
These methods all measure the occurrence rate in units of mass and semi-major
axis instead of radius and period.
Using the transit method, we do not directly measure the mass of the planet.
Instead, we must rely on a mass--radius (M--R) relationship constructed using
exoplanets with both mass and radius measurements \citep[for
example][]{Weiss:2014, Wolfgang:2016, Chen:2016} to predict the expected
masses of the transiting planets.

@@

\dfmtodo{COMPARE!}

@@

\section{Prospects for follow-up}\sectlabel{follow-up}

A real concern about the detection of exoplanets from a single transit is that
follow-up and confirmation is difficult.
Since the period of the orbit is poorly constrained and transits are sparse,
any prediction of a subsequent transit time will be too uncertain to schedule
targeted photometric follow-up.
Instead, follow-up using radial velocity and astrometry are more promising.

\hoggtodo{Comments about GAIA follow-up}
